---
title: "260_scRNA_UCell"
output: html_document
---

```{r}
library(stringr)
library(tidyverse)
library(ggplot2)
library(ggrepel)
library(cowplot)
library(viridis)
library(Seurat)
library(ggrepel)
source("src/utilities.R")
source("src/global_vars.R")
```


```{r}
seur <- readRDS("/home/user/Shared/Notebooks/Naila/Cite/multimodalAnnotatedFinal.rds")
data.seurat=seur
```


# Ucell signature scores
using cellAssign markers from this publication
```{r, fig.height=20, fig.width=20}

library(UCell)
shahlabMainCellAssignMarkers <- read_excel("../Cite/data/refrence/shahlabMainCellAssignMarkers.xlsx")

markers=as.list(shahlabMainCellAssignMarkers)

index=list()
for (i in 1:length(markers)){
  index[[i]]=markers[[i]][!is.na(markers[[i]])]
}
names(index)=colnames(shahlabMainCellAssignMarkers)

# convert to mouse gene names
# Basic function to convert human to mouse gene names
convertHumanGeneList <- function(x){
require("biomaRt")
human = useMart("ensembl", dataset = "hsapiens_gene_ensembl")
mouse = useMart("ensembl", dataset = "mmusculus_gene_ensembl")
genesV2 = getLDS(attributes = c("hgnc_symbol"), filters = "hgnc_symbol", values = x , mart = human, attributesL = c("mgi_symbol"), martL = mouse, uniqueRows=T)
humanx <- unique(genesV2[, 2])
# Print the first 6 genes found to the screen
print(head(humanx))
return(humanx)
}

httr::set_config(httr::config(ssl_verifypeer = FALSE))
finalList=list()
for( i in 1:length(index)){
  finalList[[i]]=convertHumanGeneList(index[[i]])
}

names(finalList)=colnames(shahlabMainCellAssignMarkers)

featnames=unlist(lapply(names(finalList), function(x)(paste0(x,"_UCell"))))
DefaultAssay(data.seurat)="RNA"
data.seurat <- AddModuleScore_UCell(data.seurat, features = finalList, ncores = 4)

VlnPlot(data.seurat, features = featnames, pt.size = 0)
```


save th plot
```{r}
p1=VlnPlot(data.seurat, features = featnames, pt.size = 0)
ggsave_pdf(filename = "figures/260_scRNA_UCell/PaperCellAssignMajorCelltypes.pdf",
           p1, width = 18, height = 15)

```

# Ucell with Myeliod Markers igancio's paper 
```{r, , fig.height=20, fig.width=20}
shahlabMainCellAssignMarkers <- read_excel("../Cite/data/refrence/MayeloidMarkersShah.xlsx")

markers=as.list(shahlabMainCellAssignMarkers)

index=list()
for (i in 1:length(markers)){
  index[[i]]=markers[[i]][!is.na(markers[[i]])]
}
names(index)=colnames(shahlabMainCellAssignMarkers)
httr::set_config(httr::config(ssl_verifypeer = FALSE))
convertHumanGeneList <- function(x){
require("biomaRt")
human=useEnsembl("ensembl","hsapiens_gene_ensembl", mirror = "useast")
mouse=useEnsembl("ensembl","mmusculus_gene_ensembl", mirror = "useast")
#human = useMart("ensembl", dataset = "hsapiens_gene_ensembl")
#mouse = useMart("ensembl", dataset = "mmusculus_gene_ensembl")
genesV2 = getLDS(attributes = c("hgnc_symbol"), filters = "hgnc_symbol", values = x , mart = human, attributesL = c("mgi_symbol"), martL = mouse, uniqueRows=T)
humanx <- unique(genesV2[, 2])
# Print the first 6 genes found to the screen
print(head(humanx))
return(humanx)
}
finalList=list()
for( i in 1:length(index)){
  finalList[[i]]=convertHumanGeneList(index[[i]])
}

names(finalList)=colnames(shahlabMainCellAssignMarkers)

featnames=unlist(lapply(names(finalList), function(x)(paste0(x,"_UCell"))))
DefaultAssay(data.seurat)="RNA"


data.seurat <- AddModuleScore_UCell(data.seurat, features = finalList, ncores = 4)

p2=VlnPlot(data.seurat, features = featnames, pt.size = 0)
p2
```

with multimodal clusters

```{r, , fig.height=20, fig.width=20}
Idents(data.seurat)=data.seurat$cell_type
Macro=subset(data.seurat, idents="Macrophage")
Idents(Macro)=Macro$MultimodalClusters
p3=VlnPlot(Macro, features = featnames, pt.size = 0)
p3
```


save th plotS
```{r}

ggsave_pdf(filename = "figures/260_scRNA_UCell/PaperMyeloidMacrophages.pdf",
           p3, width = 18, height = 15)

```

# UCell on my Markers List

```{r, fig.height=20, fig.width=20}

# my list of markers
myList=list()
Updatedmarkersmatrix <- read_csv("../Cite/data/refrence/Updatedmarkersmatrix.csv")
Updatedmarkersmatrix=data.frame(Updatedmarkersmatrix)
rownames(Updatedmarkersmatrix)=Updatedmarkersmatrix$...1
Updatedmarkersmatrix$...1=NULL

ind=list()
for ( i in 1:ncol(Updatedmarkersmatrix)){
  #ind[[i]]=which(Updatedmarkersmatrix%>%dplyr::select(colnames(Updatedmarkersmatrix)[i])>0)
  myList[[i]]=rownames(Updatedmarkersmatrix[which(Updatedmarkersmatrix%>%dplyr::select(colnames(Updatedmarkersmatrix)[i])>0),])
}
names(myList)=colnames(Updatedmarkersmatrix)
length(myList)# 22 sets

featnames=unlist(lapply(names(myList), function(x)(paste0(x,"_UCell"))))
#DefaultAssay(integrated)="RNA"
data.seurat <- AddModuleScore_UCell(data.seurat, features = myList, ncores = 4)

p4=VlnPlot(data.seurat, features = featnames, pt.size = 0)
p4
```


```{r, fig.height=25, fig.width=30}
Idents(data.seurat)=data.seurat$MultimodalClusters

p5=VlnPlot(data.seurat, features = featnames, pt.size = 0)
p5

```

```{r}

ggsave_pdf(filename = "figures/260_scRNA_UCell/CellAssignMarkers.pdf",
           p5, width = 25, height = 25)

```



# Compare labels

```{r, fig.height=10, fig.width=10}
tab=table(seur$MultimodalClusters, seur$cell_type)
tab <- tab/rowSums(tab)
p6=pheatmap(tab, color=viridis::viridis(100), cluster_cols=FALSE, cluster_rows=FALSE, display_numbers=T,
         number_color="white")
```

```{r, fig.height=10, fig.width=10}
tab=table(seur$cell_type, seur$cellassign)
tab <- tab/rowSums(tab)
p7=pheatmap(tab, color=viridis::viridis(100), cluster_cols=FALSE, cluster_rows=FALSE, display_numbers=T,
         number_color="white")
p7
```
the cell assign marker panel i used here wasn't good enough, it didn't include DC markers for example and included many markers, it was abit slow therefore i didn't rerun. Aslo i noticed here that although i included proliferative markers the Cycling cells were classified for TumorMetastaticHigh. this label i just took it from previous NSG T1data I clustered before.

saving the heatmaps 

```{r}
#library(grid)
pdf("figures/260_scRNA_UCell/CellAssignVsMarkersBased.pdf", height = 8, width = 8.5, paper = "letter")

setHook("grid.newpage", function() pushViewport(viewport(x=1,y=1,width=0.9, height=0.9, name="vp", just=c("right","top"))), action="prepend")
tab=table(seur$cell_type, seur$cellassign)
tab <- tab/rowSums(tab)
pheatmap(tab, color=viridis::viridis(100), cluster_cols=FALSE, cluster_rows=FALSE, display_numbers=T,
         number_color="white")
setHook("grid.newpage", NULL, "replace")
grid.text("CellAssign", y=-0.07, gp=gpar(fontsize=16))
grid.text("MarkersBased", x=-0.07, rot=90, gp=gpar(fontsize=16))
dev.off()

```

```{r}
#library(grid)
pdf("figures/260_scRNA_UCell/SubClustersVsCellType.pdf", height = 8, width = 8.5, paper = "letter")

setHook("grid.newpage", function() pushViewport(viewport(x=1,y=1,width=0.9, height=0.9, name="vp", just=c("right","top"))), action="prepend")
tab=table(seur$MultimodalClusters, seur$cell_type)
tab <- tab/rowSums(tab)
pheatmap(tab, color=viridis::viridis(100), cluster_cols=FALSE, cluster_rows=FALSE, display_numbers=T,
         number_color="white")
setHook("grid.newpage", NULL, "replace")
grid.text("CellType", y=-0.07, gp=gpar(fontsize=16))
grid.text("SubClusters", x=-0.07, rot=90, gp=gpar(fontsize=16))
dev.off()

```












